Conoco Phillips 2020

### 2020-05-28 CP_2020.Rmd

Our donor pool will consist of Conoco Phillips shock effects observed on September 11th, 2001, September 8th, 2008, and November 27, 2014. The first two shock effects were observed during recessions that were predicated by an inversion of the yiled curve, and the third was an OPEC induced supply side shock effect. Some other notable shock effects were not included in this analysis because the conditions preceding them are not simialar to those of the March 9, 2020 shock effect, among these are the October 19, 1987, August 8th, 2011, and  August 24, 2015 shock effects ([1987 Source](https://www.nber.org/chapters/c10958.pdf), [2011 Source](https://www.latimes.com/world/la-xpm-2011-aug-06-la-fi-us-debt-downgrade-20110806-story.html), [2015 Source](https://www.nytimes.com/2015/08/25/business/dealbook/daily-stock-market-activity.html)). 
<!-- 
October 19, 1987: https://www.nber.org/chapters/c10958.pdf
@article{shiller1988portfolio,
  title={Portfolio insurance and other investor fashions as factors in the 1987 stock market crash},
  author={Shiller, Robert J},
  journal={NBER Macroeconomics Annual},
  volume={3},
  pages={287--297},
  year={1988},
  publisher={MIT Press}
}

@@

## Exxon Mobile
#getSymbols('XOM', from = "1970-01-01")
#XOM <- as.data.frame(XOM)
#XOM <- XOM %>% mutate(Date = rownames(XOM))

@@

@@

```{r}
## September 11th (no trading from T-F); 1 day nowcast
COP_close <- COP %>% select(COP.Close, Date) %>% 
  rename(COP_Close = COP.Close)
GSPC_close <- GSPC %>% select(GSPC.Close, Date) %>% 
  rename(GSPC_Close = GSPC.Close)
COP_close <- merge(COP_close, GSPC_close)
Y <- COP_close$COP_Close[-1]
COP_close <- data.frame(COP_close[-nrow(COP_close), ], Y)
start <- which(COP_close$Date == "2001-09-10")
## change to equality
start_day <- as.numeric(1:nrow(COP_close) == start + 1)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-29):(start+1), ]
m_COP_9_11 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                 data = COP_close_small)
alpha_9_11_1 <- summary(m_COP_9_11)$coef[3,1:2]
alpha_9_11_1 #-1.97 (0.41) in 2020 dollars
```

@@

```{r}
m_COP_9_11 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
alpha_9_11_1_no <- summary(m_COP_9_11)$coef[3,1:2]
alpha_9_11_1_no #-1.56 (0.33) in 2020 dollars
```

Here is the 5 day nowcast with S&P 500:

```{r}
COP_close_small <- COP_close[(start-29):(start+5), ]
m_COP_9_11 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                 data = COP_close_small)
alpha_9_11_5 <- summary(m_COP_9_11)$coef[3,1:2]
             #constant: -2.19 (0.46) in 2020 dollars
alpha_9_11_5 #-1.17 (0.54) in 2020 dollars
```

Here is the 5 day nowcast without S&P 500:

```{r}
COP_close_small <- COP_close[(start-29):(start+5), ]
m_COP_9_11 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
alpha_9_11_5_no <- summary(m_COP_9_11)$coef[3,1:2]
                #constant: -1.55 (0.28) in 2020 dollars
alpha_9_11_5_no #-1.59 (0.52) in 2020 dollars
```

#### Monday, September 8th, 2008
<!-- https://www.democracynow.org/2008/9/8/headlines -->

In the weekend before trading began, the United States announced its takeover of Fannie May and Freddie Mac [Source](https://www.treasury.gov/press-center/press-releases/Pages/hp1129.aspx), and it was reported that the nation’s unemployment rate reached five-year highs. It is also worth noting that Lehman Brothers Holdings filed for bankruptcy on Monday, September 15th, 2008 with what was a record of 613 billion dollars in debt [Source](https://www.marketwatch.com/story/lehman-folds-with-record-613-billion-debt).

```{r}
COP_close <- COP_close %>% select(-"start_day")
start <- which(COP_close$Date == "2008-09-08")
## change to equality
start_day <- as.numeric(1:nrow(COP_close) == start)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-30):(start), ]
m_COP_9_08_08 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                    data = COP_close_small)
alpha_9_08_08_1 <- summary(m_COP_9_08_08)$coef[3,1:2]
alpha_9_08_08_1 #-6.95 (1.98) in 2020 dollars
```

```{r}
m_COP_9_08_08 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
alpha_9_08_08_1_no <- summary(m_COP_9_08_08)$coef[3,1:2]
alpha_9_08_08_1_no #-6.94 (1.94) in 2020 dollars
```

Here is the 5 day nowcast with S&P 500:

```{r}
COP_close_small <- COP_close[(start-30):(start+4), ]
m_COP_9_08_08 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                    data = COP_close_small)
alpha_9_08_08_5 <- summary(m_COP_9_08_08)$coef[3,1:2]
                #constant: -4.20 (1.61) in 2020 dollars
alpha_9_08_08_5 # -6.28 (2.00) in 2020 dollars
```

Here is the 5 day nowcast with S&P 500:

```{r}
m_COP_9_08_08 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
alpha_9_08_08_5_no <- summary(m_COP_9_08_08)$coef[3,1:2]
                   #constant: -4.14 (1.58) in 2020 dollars
alpha_9_08_08_5_no #-6.26 (1.94) 
```

@@

```{r}
COP_close <- COP_close %>% select(-"start_day")
start <- which(COP_close$Date == "2014-11-26")
start_day <- as.numeric(1:nrow(COP_close) == start)
## change to equality
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-30):(start), ]
m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day + GSPC_Close,
                    data = COP_close_small)
alpha_11_27_14_1 <- summary(m_COP_11_27_14)$coef[3,1:2]
alpha_11_27_14_1 #-5.68 (1.06) in 2020 dollars
```

```{r}
m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
alpha_11_27_14_1_no <- summary(m_COP_11_27_14)$coef[3,1:2]
alpha_11_27_14_1_no #-5.26 (0.97) in 2020 dollars
```

Here is the 5 day nowcast with S&P 500:

```{r}
COP_close_small <- COP_close[(start-30):(start+4), ]
m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day + GSPC_Close,
                    data = COP_close_small)
alpha_11_27_14_5 <- summary(m_COP_11_27_14)$coef[3,1:2]
                 #constant: -2.69 (0.94) in 2020 dollars
alpha_11_27_14_5 #-5.43 (1.01) in 2020 dollars
```

Here is the 5 day nowcast without S&P 500:

```{r}
m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
alpha_11_27_14_5_no <- summary(m_COP_11_27_14)$coef[3,1:2]
                    #constant:-1.23 (0.65) in 2020 dollars
alpha_11_27_14_5_no #-5.26 (0.99) in 2020 dollars
```

@@

```{r}
m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                    data = COP_close_small)
alpha_03_09_20_1 <- summary(m_COP_03_09_20)$coef[3,1:2]
alpha_03_09_20_1 #-10.51414 (1.62901)
```

@@

```{r}
m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
alpha_03_09_20_1_no <- summary(m_COP_03_09_20)$coef[3,1:2]
alpha_03_09_20_1_no #-10.533756 (1.617991)
```

Here is the 5 day shock effect with S&P 500:

```{r}
COP_close_small <- COP_close[(start-30):(start+4), ]
m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                    data = COP_close_small)
alpha_03_09_20_5 <- summary(m_COP_03_09_20)$coef[3,1:2]
                 #constant: -5.333522 (2.077089)
alpha_03_09_20_5 #-10.714979 (1.775454)
```

Here is the 5 day shock effect without S&P 500:

```{r}
m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
alpha_03_09_20_5_no <- summary(m_COP_03_09_20)$coef[3,1:2]
                    #constant: -5.314242 (2.031455)
alpha_03_09_20_5_no #-10.668604 (1.754461)
```

@@

```{r}
a_estimates <- rbind(
c(-1.97, 0.41, -1.56, 0.33, -1.17, 0.54, -1.59, 0.52),
c(-6.95, 1.98, -6.94, 1.94, -6.28, 2.00, -6.26, 1.94),
c(-5.68, 1.06, -5.26, 0.97, -5.43, 1.01, -5.26, 0.99)
)
colnames(a_estimates) <- c("a_1","sd_a_1","a_1_no","sd_a_1_no",
                   "a_5","sd_a_5","a_5_no","sd_a_5_no")
rownames(a_estimates) <- c("y2001", "y2008", "y2014")
```

@@

```{r}
a_adj <- colMeans(a_estimates[,1:4 * 2 -1 ])
a_adj_no911 <- colMeans(a_estimates[-1,1:4 * 2 -1 ])
weights <- rbind(
(1 / a_estimates[,1:4 * 2])[1, ] / colSums(1 / a_estimates[,1:4 * 2]),
(1 / a_estimates[,1:4 * 2])[2, ] / colSums(1 / a_estimates[,1:4 * 2]),
(1 / a_estimates[,1:4 * 2])[3, ] / colSums(1 / a_estimates[,1:4 * 2])
)
a_adj_IVW <- colSums(weights * a_estimates[,1:4 * 2 -1 ])
weights_no911 <- rbind(
(1 / a_estimates[-1,1:4 * 2])[1, ] / colSums(1 / a_estimates[-1,1:4 * 2]),
(1 / a_estimates[-1,1:4 * 2])[2, ] / colSums(1 / a_estimates[-1,1:4 * 2])
)
a_adj_IVW_no911 <- colSums(weights_no911 * a_estimates[-1,1:4 * 2 -1 ])
```

@@

Interesting to note that the March 9th, 2020 shock effect is closely approximated by the additive effect of the recession diven shock on September 8th, 2008 and the OPEC supply driven shock on November 27, 2014.

```{r}
additive <- colSums(a_estimates[-1,1:4 * 2 -1])
additive
```

@@

```{r}
m_COP_03_06_20 <- lm(Y ~ COP_Close + GSPC_Close, 
                     data = COP_close_small[-nrow(COP_close_small), ])
preds <- predict(m_COP_03_06_20)
Yhat_nothing_1 <- 0.933928 * 46.96604 -7.462690 + 0.003267 * 3023.94
Yhat_adj_1 <- Yhat_nothing_1 + shock_effects[, 1]
Yhat_adj_additive_1 <- Yhat_nothing_1 + additive[1]

## doing nothing completely misses the mark
Yhat_nothing_1 - COP_close_small$Y[nrow(COP_close_small)]

## adjustment gets closer
Yhat_adj_1 - COP_close_small$Y[nrow(COP_close_small)]

## additive effect does well
Yhat_adj_additive_1 - COP_close_small$Y[nrow(COP_close_small)]
```

```{r}
COP_close_small$id <- 1:nrow(COP_close_small)
mat <- cbind(COP_close_small$id[nrow(COP_close_small)], 
             c(Yhat_adj_1, Yhat_adj_additive_1))
colnames(mat) <- c("id", "Yhat_adj")
dat <- as.data.frame(mat)
ggplot(COP_close_small, mapping = aes(x = id, y = Y)) + 
  labs(title = "Conoco Phillips forecasting (with S&P 500)", 
       x = "Day", y = "Close price (in USD)") +
  geom_point() + 
  geom_point(data = dat, aes(x = id, y = Yhat_adj), col = 2, pch = 2:6) + 
  geom_line(aes(x = id, y = c(m_COP_03_06_20$fitted.values, Yhat_nothing_1)), 
            col = "blue") +
  theme_minimal()
```

```{r}
m_COP_03_06_20 <- lm(Y ~ COP_Close, 
                     data = COP_close_small[-nrow(COP_close_small), ])
summary(m_COP_03_06_20)
preds <- predict(m_COP_03_06_20)
Yhat_nothing_1_no <- -1.25682 + 1.01170 * 47.00149 
Yhat_adj_1_no <- Yhat_nothing_1_no + shock_effects[, 2]
Yhat_adj_additive_1_no <- Yhat_nothing_1_no + additive[2]

## doing nothing misses the mark
Yhat_nothing_1_no - COP_close_small$Y[nrow(COP_close_small)]

## adjustment gets closer
Yhat_adj_1_no - COP_close_small$Y[nrow(COP_close_small)]

## additive effect does well
Yhat_adj_additive_1_no - COP_close_small$Y[nrow(COP_close_small)]
```

```{r}
COP_close_small$id <- 1:nrow(COP_close_small)
mat <- cbind(COP_close_small$id[nrow(COP_close_small)], 
             c(Yhat_adj_1,  Yhat_adj_additive_1_no))
colnames(mat) <- c("id", "Yhat_adj")
dat <- as.data.frame(mat)
ggplot(COP_close_small, mapping = aes(x = id, y = Y)) + 
  labs(title = "Conoco Phillips forecasting (without S&P 500)", 
       x = "Day", y = "Close price (in USD)") +
  geom_point() + 
  geom_point(data = dat, aes(x = id, y = Yhat_adj), 
                             col = 2, pch = 2:6) + 
  geom_line(aes(x = id, y = c(m_COP_03_06_20$fitted.values,
                              Yhat_nothing_1_no)), 
            col = "blue") +
  theme_minimal()
```

>>>>

Our donor pool will consist of Conoco Phillips shock effects observed on September 11th, 2001, March 18th, 2008, many days in September and October of 2008, and November 27, 2014. The September 11th, 2001 and the 2008 shock effects were observed during recessions that were predicated by an inversion of the yield curve, and the November 27, 2014 shock was an OPEC induced supply side shock effect. <!--Some other notable shock effects were not included in this analysis because the conditions preceding them are not simialar to those of the March 9, 2020 shock effect, among these are the October 19, 1987, August 8th, 2011, and  August 24, 2015 shock effects ([1987 Source](https://www.nber.org/chapters/c10958.pdf), [2011 Source](https://www.latimes.com/world/la-xpm-2011-aug-06-la-fi-us-debt-downgrade-20110806-story.html), [2015 Source](https://www.nytimes.com/2015/08/25/business/dealbook/daily-stock-market-activity.html)). --> 
<!-- 
October 19, 1987: https://www.nber.org/chapters/c10958.pdf
@article{shiller1988portfolio,
  title={Portfolio insurance and other investor fashions as factors in the 1987 stock market crash},
  author={Shiller, Robert J},
  journal={NBER Macroeconomics Annual},
  volume={3},
  pages={287--297},
  year={1988},
  publisher={MIT Press}
}

@@

## Brent Crude prices
Brent_Crude <- read.csv("https://pkgstore.datahub.io/core/oil-prices/brent-daily_csv/data/d93216330ab2c27aae3d177b2f0f0921/brent-daily_csv.csv") %>%
  rename(Oil_Close = Price)

## WTI Crude prices
WTI_Crude <- read.csv("https://pkgstore.datahub.io/core/oil-prices/wti-daily_csv/data/c414c9d375ec3c8f9d7c276d866fb2a4/wti-daily_csv.csv") %>%
  rename(WTI_Close = Price)

## inflation adjustment
getSymbols("CPIAUCSL", src='FRED')
avg.cpi <- apply.yearly(CPIAUCSL, mean)
inflation_adj <- as.numeric(avg.cpi['2020'])/avg.cpi
inflation_adj <- as.data.frame(inflation_adj)
colnames(inflation_adj) <- c("dollars_2020")
inflation_adj <- inflation_adj %>% mutate(year = 1947:2020)
```

```{r, echo = FALSE, eval = FALSE}
## Exxon Mobile
#getSymbols('XOM', from = "1970-01-01")
#XOM <- as.data.frame(XOM)
#XOM <- XOM %>% mutate(Date = rownames(XOM))

@@

Here is the estimated shock effect 1 day in the future with covariates:

```{r}
## September 11th (no trading from T-F); 1 day nowcast
COP_close <- COP %>% select(COP.Close, Date) %>% 
  rename(COP_Close = COP.Close)
GSPC_close <- GSPC %>% select(GSPC.Close, Date) %>% 
  rename(GSPC_Close = GSPC.Close)
COP_close <- merge(COP_close, GSPC_close)
COP_close <- merge(COP_close, WTI_Crude)
Y <- COP_close$COP_Close[-1]
COP_close <- data.frame(COP_close[-nrow(COP_close), ], Y)
start <- which(COP_close$Date == "2001-09-10")
start_day <- as.numeric(1:nrow(COP_close) == start + 1)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-29):(start+1), ]
m_COP_9_11 <- lm(Y ~ COP_Close + start_day + GSPC_Close + WTI_Close, 
                 data = COP_close_small)
alpha_9_11 <- summary(m_COP_9_11)$coef[3,1:2] * 
  inflation_adj$dollars_2020[inflation_adj$year == 2001] 
alpha_9_11
```

Here is the estimated shock effect 1 day in the future without covariates:

```{r}
m_COP_9_11_no <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
alpha_9_11_no <- summary(m_COP_9_11_no)$coef[3,1:2] * 
  inflation_adj$dollars_2020[inflation_adj$year == 2001] 
alpha_9_11_no
```

#### 2008 shock effects
<!-- https://www.democracynow.org/2008/9/8/headlines -->

The first 4 major shocks of 2008 were proceeded by unprecedented failures in the financial sector that rattled markets, oil prices, and Conoco Phillips stock alike. The March 8th, September 12th, and September 26th shock effects were proceeded by the bailouts or failures of Bear Stearns, Lehman Brothers, and Washington Mutual financial institutions. The September 8th shock effect was proceeded by Fannie Mae and Freddie Mac being placed in conservatorship.

We first find the Baer Stearns shock effect. Here is the estimated shock effect 1 day in the future with covariates:

```{r}
COP_close <- COP_close %>% select(-"start_day")
start <- which(COP_close$Date == "2008-03-18")
start_day <- as.numeric(1:nrow(COP_close) == start)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-29):(start+1), ]
m_COP_3_18 <- lm(Y ~ COP_Close + start_day + GSPC_Close + WTI_Close, 
                 data = COP_close_small)
alpha_3_18 <- summary(m_COP_3_18)$coef[3,1:2] * 
  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
alpha_3_18
```

Here is the estimated shock effect 1 day in the future without covariates:

```{r}
m_COP_3_18_no <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
alpha_3_18_no <- summary(m_COP_3_18_no)$coef[3,1:2] * 
  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
alpha_3_18_no
```

We now find the September shock effects. We estimate the financial instistution failures as if they are all the same.

```{r}
COP_close <- COP_close %>% select(-"start_day")
COP_close[which(COP_close$COP_Close - COP_close$Y >= 3.5), ][2:4, ]
start <- which(COP_close$COP_Close - COP_close$Y >= 3.5)[2:4]
start_day <- as.numeric(1:nrow(COP_close) %in% start)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[
  which(COP_close$Date == "2008-07-28"):which(COP_close$Date == "2008-09-26"), ]
m_COP_Sept_08 <- lm(Y ~ COP_Close + start_day + GSPC_Close + WTI_Close, 
                 data = COP_close_small)
alpha_Sept_08 <- summary(m_COP_Sept_08)$coef[3,1:2] * 
  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
alpha_Sept_08
```

Here is the estimated shock effect 1 day in the future without covariates:

```{r}
m_COP_Sept_08_no <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
alpha_Sept_08_no <- summary(m_COP_Sept_08_no)$coef[3,1:2] * 
  inflation_adj$dollars_2020[inflation_adj$year == 2008] 
alpha_Sept_08_no
```

<!-- In the weekend before trading began, the United States announced its takeover of Fannie May and Freddie Mac [Source](https://www.treasury.gov/press-center/press-releases/Pages/hp1129.aspx), and it was reported that the nation’s unemployment rate reached five-year highs. It is also worth noting that Lehman Brothers Holdings filed for bankruptcy on Monday, September 15th, 2008 with what was a record of 613 billion dollars in debt [Source](https://www.marketwatch.com/story/lehman-folds-with-record-613-billion-debt).

@@

```{r}
COP_close <- COP_close %>% select(-"start_day")
#start <- which(COP_close$Date == "2008-09-08")
start <- which(COP_close$Date == "2008-09-12")

## change to equality
start_day <- as.numeric(1:nrow(COP_close) == start)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-30):(start), ]
m_COP_9_08_08 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                    data = COP_close_small)
alpha_9_08_08_1 <- summary(m_COP_9_08_08)$coef[3,1:2]
alpha_9_08_08_1 #-6.95 (1.98) in 2020 dollars
```

@@

```{r}
m_COP_9_08_08 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
alpha_9_08_08_1_no <- summary(m_COP_9_08_08)$coef[3,1:2]
alpha_9_08_08_1_no #-6.94 (1.94) in 2020 dollars
```
-->

@@

Here is the estimated shock effect 1 day in the future with covariates:

```{r}
COP_close <- COP_close %>% select(-"start_day")
start <- which(COP_close$Date == "2014-11-26")
start_day <- as.numeric(1:nrow(COP_close) == start)
COP_close <- COP_close %>% mutate(start_day = start_day)
COP_close_small <- COP_close[(start-30):(start), ]
m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day + GSPC_Close,
                    data = COP_close_small)
alpha_11_27_14 <- summary(m_COP_11_27_14)$coef[3,1:2] * 
  inflation_adj$dollars_2020[inflation_adj$year == 2014] 
alpha_11_27_14
```

Here is the estimated shock effect 1 day in the future without covariates:

```{r}
m_COP_11_27_14 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
alpha_11_27_14_no <- summary(m_COP_11_27_14)$coef[3,1:2]  * 
  inflation_adj$dollars_2020[inflation_adj$year == 2014] 
alpha_11_27_14_no
```

@@

```{r}
m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day + GSPC_Close, 
                    data = COP_close_small)
alpha_03_09_20 <- summary(m_COP_03_09_20)$coef[3,1:2]
alpha_03_09_20 #-10.51414 (1.62901)
```

@@

```{r}
m_COP_03_09_20 <- lm(Y ~ COP_Close + start_day, data = COP_close_small)
alpha_03_09_20_no <- summary(m_COP_03_09_20)$coef[3,1:2]
alpha_03_09_20_no #-10.533756 (1.617991)
```

@@

```{r}

a_estimates <- rbind( c(alpha_9_11, alpha_9_11_no),
  c(alpha_3_18, alpha_3_18_no),
  c(alpha_Sept_08, alpha_Sept_08_no),
  c(alpha_11_27_14, alpha_11_27_14_no))
colnames(a_estimates) <- c("a_1","sd_a_1","a_1_no","sd_a_1_no")
rownames(a_estimates) <- c("y2001", "my2008", "sy2008", "y2014")
```

@@

```{r}
a_adj <- colMeans(a_estimates[, c(1,3)])
a_adj_no911 <- colMeans(a_estimates[-1, c(1,3)])
weights <- rbind(
(1 / a_estimates[, c(2,4)])[1, ] / colSums(1 / a_estimates[, c(2,4)]),
(1 / a_estimates[, c(2,4)])[2, ] / colSums(1 / a_estimates[, c(2,4)]),
(1 / a_estimates[, c(2,4)])[3, ] / colSums(1 / a_estimates[, c(2,4)]),
(1 / a_estimates[, c(2,4)])[4, ] / colSums(1 / a_estimates[, c(2,4)])
)
a_adj_IVW <- colSums(weights * a_estimates[, c(1,3)])
weights_no911 <- rbind(
(1 / a_estimates[-1, c(2,4)])[1, ] / colSums(1 / a_estimates[-1, c(2,4)]),
(1 / a_estimates[-1, c(2,4)])[2, ] / colSums(1 / a_estimates[-1, c(2,4)]),
(1 / a_estimates[-1, c(2,4)])[3, ] / colSums(1 / a_estimates[-1, c(2,4)])
)
a_adj_IVW_no911 <- colSums(weights_no911 * a_estimates[-1, c(1,3)])
```

@@

Interesting to note that the March 9th, 2020 shock effect is closely approximated by the additive effect of the average of the 2008 recession diven shocks and the OPEC supply driven shock on November 27, 2014.

```{r}
additive <- colMeans(a_estimates[c(2,3), c(1,3)]) + a_estimates[4, c(1,3)]
additive
```

@@

```{r}
m_COP_03_06_20 <- lm(Y ~ COP_Close + GSPC_Close + WTI_Close, 
                     data = COP_close_small[-nrow(COP_close_small), ])
preds <- predict(m_COP_03_06_20)
summary(m_COP_03_06_20)
Yhat_nothing <- -2.430990 + 1.045492 * 47.01888 + 
  0.003063 * 3023.94 + -0.210924 * 45.90
Yhat_adj <- Yhat_nothing + shock_effects[, 1]
Yhat_adj_additive <- Yhat_nothing + additive[1]

## doing nothing completely misses the mark
Yhat_nothing - COP_close_small$Y[nrow(COP_close_small)]

## adjustment gets closer
Yhat_adj - COP_close_small$Y[nrow(COP_close_small)]

## additive effect does well
Yhat_adj_additive - COP_close_small$Y[nrow(COP_close_small)]
```

```{r}
COP_close_small$id <- 1:nrow(COP_close_small)
mat <- cbind(COP_close_small$id[nrow(COP_close_small)], 
             c(Yhat_adj, Yhat_adj_additive))
colnames(mat) <- c("id", "Yhat_adj")
dat <- as.data.frame(mat)
ggplot(COP_close_small, mapping = aes(x = id, y = Y)) + 
  labs(title = "Conoco Phillips forecasting (with S&P 500)", 
       x = "Day", y = "Close price (in USD)") +
  geom_point() + 
  geom_point(data = dat, aes(x = id, y = Yhat_adj), col = 2, pch = 2:6) + 
  geom_point(data = data.frame(x = unique(dat$id), y =Yhat_nothing), 
             aes(x = x, y = y), col = "blue", cex = 1.5) + 
  geom_line(aes(x = id, y = c(m_COP_03_06_20$fitted.values, Yhat_nothing)), 
            col = "blue") + 
    annotate("text", x=1, y=seq(from = 47, to = 39,length.out=6), 
             label=c("no adjustment","mean adjustment",
                     "mean adjustment (no 9/11)","IVW adjustment",
                     "IVW adjustment (no 9/11)", "aggregate adjustment"), 
             hjust=0) + 
    annotate("point", x = 0, y=seq(from = 47, to = 39,length.out=6), 
             pch = c(16,2:6),
             color = c("blue","red","red","red","red","red")) +
  theme_minimal()
```

Here is the 1 day nowcast without covariates:

```{r}
m_COP_03_06_20 <- lm(Y ~ COP_Close, 
                     data = COP_close_small[-nrow(COP_close_small), ])
summary(m_COP_03_06_20)
preds <- predict(m_COP_03_06_20)
Yhat_nothing_no <- -1.25682 + 1.01170 * 47.00149
Yhat_adj_no <- Yhat_nothing_no + shock_effects[, 2]
Yhat_adj_additive_no <- Yhat_nothing_no + additive[2]

## doing nothing misses the mark
Yhat_nothing_no - COP_close_small$Y[nrow(COP_close_small)]

## adjustment gets closer
Yhat_adj_no - COP_close_small$Y[nrow(COP_close_small)]

## additive effect does well
Yhat_adj_additive_no - COP_close_small$Y[nrow(COP_close_small)]
```

```{r}
COP_close_small$id <- 1:nrow(COP_close_small)
mat <- cbind(COP_close_small$id[nrow(COP_close_small)], 
             c(Yhat_adj,  Yhat_adj_additive_no))
colnames(mat) <- c("id", "Yhat_adj")
dat <- as.data.frame(mat)
ggplot(COP_close_small, mapping = aes(x = id, y = Y)) + 
  labs(title = "Conoco Phillips forecasting (without S&P 500)", 
       x = "Day", y = "Close price (in USD)") +
  geom_point() + 
  geom_point(data = dat, aes(x = id, y = Yhat_adj), 
                             col = 2, pch = 2:6) + 
  geom_point(data = data.frame(x = unique(dat$id), y =Yhat_nothing_no), 
             aes(x = x, y = y), col = "blue", cex = 1.5) + 
  geom_line(aes(x = id, y = c(m_COP_03_06_20$fitted.values,
                              Yhat_nothing_no)), 
            col = "blue") +
      annotate("text", x=1, y=seq(from = 47, to = 39,length.out=6), 
             label=c("no adjustment","mean adjustment",
                     "mean adjustment (no 9/11)","IVW adjustment",
                     "IVW adjustment (no 9/11)", "aggregate adjustment"), 
             hjust=0) + 
    annotate("point", x = 0, y=seq(from = 47, to = 39,length.out=6), 
             pch = c(16,2:6),
             color = c("blue","red","red","red","red","red")) +
  theme_minimal()
```
